Verifying Demonstrations

### 2020-02-25 paper/DB-Schnorr-UWB.tex
Clarifies comment on Brands-Chaum

The protocol is also secure against distance hijacking due to the fact that the 
authenticating bit string is used during the \ac{DB} phase, not the challenge 
bit string, as is the case for the original protocol of Brands-Chaum.
\Ac{DBDH} requires that the adversary finds a collision between his response 
and that of the honest prover.
Thus the probability of success is equivalent to a collision for the responses 
for the chosen challenge --- in each round.

>>>>

The protocol is also secure against distance hijacking due to the fact that the 
authenticating bit string is used during the \ac{DB} phase.
(Brands-Chaum used the challenge bit string, something that made their protocol 
vulnerable.)
\Ac{DBDH} requires that the adversary finds a collision between his response 
and that of the honest prover.
Thus the probability of success is equivalent to a collision for the responses 
for the chosen challenge --- in each round.
